---
title: "Week7_Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
For Questions 1-6, use the cats dataset from the MASS package.

Q1. Consider three models:

Simple: $Y = \beta_0 + \beta_1 x_1 + \epsilon$

Additive: $Y = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \epsilon$

Interaction: $Y = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_1 x_2 + \epsilon$

where

Y is the heart weight of a cat in grams
x_1 is the body weight of a cat in kilograms
x_2 is a dummy variable that takes the value 1 when a cat is male

Use the simple model to estimate the change in average heart weight when body weight is increased by 1 kilogram, for a female cat.
```{r}
library(MASS)
coef(lm(Hwt~Bwt, data=cats))[2]
```

q2. Use the interaction model to estimate the change in average heart weight when body weight is increased by 1 kilogram, for a female cat.

```{r}

coef(lm(Hwt~0+Sex+Bwt:Sex, data=cats))[3]

```

Q3. Use the interaction model to estimate the change in average heart weight when body weight is increased by 1 kilogram, for a male cat.

```{r}
coef(lm(Hwt~0+Sex+Bwt:Sex, data=cats))[4]
```

Q4. Use the additive model to estimate the difference in the change in average heart weight when body weight is increased by 1 kilogram between a male and female cat.

```{r}
coef(lm(Hwt~Bwt+Sex, data=cats))
# No change in slope hence answer is 0
```

Q5. Use an F test to compare the additive and interaction models. Report the value of the F test statistic.
```{r}
interactive_m <- lm(Hwt~Bwt*Sex, data = cats)
additive_m <- lm(Hwt~Bwt+Sex, data = cats)
anova(additive_m, interactive_m)$F
```
Q6. Carry out the test in Question 5 using α=0.05. Based on this test, which model is preferred?

* Simple
* Additive
* Interaction
* None of the above

```{r}
simple_m <- lm(Hwt~Bwt, data=cats)
interactive_m <- lm(Hwt~Bwt*Sex, data = cats)
anova(simple_m, additive_m)$`Pr(>F)`[2]

additive_m <- lm(Hwt~Bwt+Sex, data = cats)
anova(simple_m, interactive_m)$`Pr(>F)`[2]
anova(additive_m, interactive_m)$`Pr(>F)`[2]
# to do Why is the answer Interactive
```
Answer Simple # Wrong answer
Correct Answer: interactive



For Questions 7-13, use the iris dataset which is built into R. Use ?iris to learn about this dataset. (Note that this model would be somewhat odd in practice. Usually it would make sense to predict species from characteristics, or characteristics from species. Here we’re using a combination of characteristics and species to predict other characteristics, for illustrative purposes.)


Q7. Using the model fit with the given code, predict the sepal length of a versicolor with a petal length of 5.10.

iris_add = lm(Sepal.Length ~ Petal.Length + Species, data = iris)

```{r}
iris_add = lm(Sepal.Length ~ Petal.Length + Species, data = iris)
predict(iris_add, newdata = data.frame("Species"="versicolor", "Petal.Length"=5.10))
```


Q8. Continue to use the model from Question 7. Create a 90% confidence interval for the difference in mean sepal length between virginicas and setosas for a given petal length. Report the lower bound of this interval

```{r}
iris_add = lm(Sepal.Length ~ Petal.Length + Species, data = iris)

confint(iris_add, level=.9)[4,]
```

Q9. Continue to use the model from Question 7. Perform a test that compares this model to one without an effect for species. Report the value of the test statistic for this test.

```{r}
iris_add = lm(Sepal.Length ~ Petal.Length + Species, data = iris)
iris_add_null = lm(Sepal.Length ~ Petal.Length, data = iris)
anova(iris_add_null,iris_add)$F[2]

```

Q10. Now consider the model with the interaction given above. Excluding $\sigma^2$, how many parameters does this model have? Stated another way, if written mathematically, how many β parameters are in the model?

```{r}
iris_int = lm(Sepal.Length ~ Petal.Length * Species, data = iris)
length(coef(iris_int))

```

Q11. Using the interaction model fit with the given code, create a 99% prediction interval for the sepal length of a versicolor with a petal length of 5.10. Report the upper bound of this interval.
```{r}
iris_int = lm(Sepal.Length ~ Petal.Length * Species, data = iris)
newdata = data.frame("Species"="versicolor", "Petal.Length" = c(5.10))
predict(iris_int, interval = c("prediction"), level=.99, newdata = newdata)

```

Q12. Using the interaction model fit with the given code, obtain an estimate of the change in mean sepal length for a petal length increase of 1 unit, for a versicolor.
```{r}
iris_int = lm(Sepal.Length ~ Petal.Length * Species, data = iris)
coef(iris_int)[2]+coef(iris_int)[5]

iris_int2 = lm(Sepal.Length ~ 0 + Species + Petal.Length:Species, data = iris)
coef(iris_int2)


```

Q13. Compare the two previous models, the additive and interaction models, using an ANVOA F test using α=0.01. Based on this test, which model is preferred?

```{r}
iris_add = lm(Sepal.Length ~ Petal.Length + Species, data = iris)
iris_int = lm(Sepal.Length ~ Petal.Length * Species, data = iris)

anova(iris_add, iris_int)$`Pr(>F)`[2]

```
Answer: additive

For Questions 14-15, use the swiss dataset, which is built into R.

Q14. Fit a multiple linear model with Fertility as the response and Education, Catholic, and Infant.Mortality as predictors. Use the first order terms as well as all two- and three-way interactions.

Use this model to estimate the change in mean Fertility for an increase of Education of one unit when Catholic is 90.0 and Infant.Mortality is 20.0.

```{r}
swiss_int <- lm(Fertility~Education*Catholic*Infant.Mortality, data=swiss) 
newdata=data.frame(Education=c(10,11), Catholic=c(90.0,90.0), Infant.Mortality=c(20.0,20.0))
diff(predict(swiss_int, newdata = newdata))

```

Q15. Test for the significance of the three-way interaction in the model from Question 14. Report the p-value of this test.
```{r}
swiss_int <- lm(Fertility~Education*Catholic*Infant.Mortality, data=swiss) 
swiss_int_2 <- lm(Fertility~(Education+Catholic+Infant.Mortality)^2, data=swiss) 
anova(swiss_int_2, swiss_int)$`Pr(>F)`[2]

```

