---
title: "R Notebook"
output: html_notebook
---

```{r}
3^(-6)
3^6
pi
exp(1)
log(exp(1))
log(10)
c(1:10)
c(seq(.1,.9,.1))

c(rep(1,5),6)
```
```{r}
x = c(seq(1,7,2),8:9)
x
x[1]
x[-1]
x[-4]
```
```{r}
x= 1:10
x=x*2
x
x^2
2^x
log(x)
x[x>3]
x[4:9]
sum(x)
sum(x[x>18])
as.character.POSIXt(x)

which(x>8)
x[which(x>8)]
max(x)
which(x==max(x))
rep(2,6)
```
```{r}
x=c(1,3,5,7,8,9)
y=1:60
x+y
length(rep(x,10))
```

```{r}
x=1:9
y=9:1

X = rbind(x,y)
X
Y = cbind(x,y)
Y
```
```{r}
x=1:9
y=rev(x)
X= matrix(x,3,3,byrow=TRUE)
Y=matrix(y,3,3,byrow=TRUE)
X
Y
X%*%Y
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

