---
title: "Week9 Practice Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
quiz_data <- read.csv("quiz_data.csv")
```


Q1. From quiz_data.csv Calculate the partial correlation coefficient between y and x1 controlling for the effect of the remaining variables.

```{r}
m1 <- lm(y~ . - x1 , data=quiz_data)
m2 <- lm(x1~ . - y , data = quiz_data)

cor(resid(m2), resid(m1))
```

Q2. The above code block has access to a data frame stored in the variable quiz_data. We will use y as the response. Fit an additive model using the remaining variables as predictors. Calculate the variance inflation factor of the regression coefficient for x5.

```{r}
m1 <- lm(y~., data = quiz_data)
car::vif(m1)
```

Q3. The above code block has access to a data frame stored in the variable quiz_data. We will use y as the response. Fit two additive linear models:

* One with all possible predictors
* One with x1, x2, and x3 as predictors
Use AIC to compare these two models. Report the RSS of the preferred model.

```{r}
m1 <- lm(y~., data = quiz_data)
m2 <- lm(y~x1+x2+x3, data = quiz_data)

extractAIC(m1)
extractAIC(m2)
sum(resid(m1)^2)

```

Q4. The above code block has access to a data frame stored in the variable quiz_data. We will use y as the response. Fit two additive linear models:

* One with x1, x2, and x4 as predictors
* One with x3, x4, x5, and x6 as predictors
Report the Adjusted R^2 of the model with the better Adjusted R^2

```{r}

m1 <- lm(y~x1+x2+x4, data = quiz_data)
m2 <- lm(y~x3+x4+x5+x6, data = quiz_data)

summary(m1)$"adj.r.squared"
summary(m2)$"adj.r.squared" 
# LARGER adjusted R2 is better

```

Q5. The above code block has access to a data frame stored in the variable quiz_data. We will use y as the response. Start with an additive model using the remaining variables as predictors, then perform variable selection using backwards AIC.

Report the LOOCV-RMSE of the chosen mode.

```{r}
m1 <- lm(y~., data = quiz_data)

frm <- formula(step(m1, direction = "backward", trace = 0))

m2 <- lm(formula=frm, data = quiz_data)


sqrt(mean((resid(m2) / (1 - hatvalues(m2))) ^ 2))

```

