---
title: "Week10 Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. Consider a categorical response Y which takes possible values 0 and 1 as well as three numerical predictors X_1, X_2 and X_3. Recall that

$p({\bf x}) = P[Y = 1 \mid {\bf X} = {\bf x}]$

Consider the model

$\log\left(\frac{p({\bf x})}{1 - p({\bf x})}\right) = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3$
 

together with parameters

\beta_0 = -3
\beta_1 = 1
\beta_2 = 2
\beta_2 = 3

Calculate $P[Y = 0 \mid X_1 = -1, X_2 = 0.5, X_2 = 0.25]$

```{r}
p_y_1 <- 1/(1 + exp(-1 * (-3 + (-1*1) + (2 * .5) + (3 * .25))))
1- p_y_1
```

Q2. For Exercises 2 - 7, use the built-in R dataset mtcars. We will use this dataset to attempt to predict whether or not a car has a manual transmission.

Recall that

$p({\bf x}) = P[Y = 1 \mid {\bf X} = {\bf x}]$

Fit the model

$\log\left(\frac{p({\bf x})}{1 - p({\bf x})}\right) = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3$
 

where

Y is am
X_1 is mpg
X_2 is hp
X_3 is qsec
Report the value of the estimate for \beta_3

```{r}

```

