---
title: "Week2_Pracice Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Q1.
Consider a random variable X that has a normal distribution with a mean of 5 and a variance of 9.

Calculate P[X > 4]P[X>4].
```{r}
pnorm(4, mean=5, sd=3, lower.tail = FALSE)

```

Q2. Consider the simple linear regression model Y=−3+2.5x+ϵ

where  ϵ∼N(0,σ^2=4)

What is the expected value of Y given that x = 5? That is, what is E[Y∣X=5]
```{r}
(y = -3+2.5*5)
```

Q3. Given the SLR model in Question 2, what is the standard deviation of Y when x is 10? That is, what is SD[Y∣X=10]?
```{r}
(sd = sqrt(4))
```

Q4. For this question, use the built-in trees dataset in R. Fit a simple linear regression model with Girth as the response and Height as the predictor.

What is the slope of the fitted regression line?

```{r}
lm(Girth~Height, data=trees)

```

Q5. Continue using the SLR model you fit in Question 4. What is the value of R^2
  for this fitted SLR model?
  
```{r}
summary(lm(Girth~Height, data=trees))
# Choose multiple R-squared value
```

