---
title: "Week2_Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. Consider the simple linear regression model Y=10+5x+ϵ
where ϵ∼N(0,σ^2=16)
Calculate the probability that Y is less than 6 given that x = 0

```{r}
pnorm(6, mean=(10+5*0), sd=4)
```
Q2. Using the SLR model in Question 1, what is the probability that YY is greater than 3 given that x = -1
```{r}
pnorm(3, mean=(10+5*-1), sd=4, lower.tail=FALSE)
```

Q3. Using the SLR model in Question 1, what is the probability that YY is greater than 3 given that x = -2

```{r}
pnorm(3, mean=(10+5*-2), sd=4, lower.tail=FALSE)
```

For Questions 4-11, use the faithful dataset, which is built into R.


Q4. Suppose we would like to predict the duration of an eruption of the Old Faithful geyser in Yellowstone National Park based on the waiting time before an eruption. Fit a simple linear model in R that accomplishes this task.

What is the estimate of the intercept parameter?
```{r}
faithful_lm <- lm(eruptions~waiting, data=faithful)
faithful_lm
```
Q5. What is the estimate of the slope parameter?
```{r}
coefficients(faithful_lm)
```

Q6. Use the fitted model to predict the duration of an eruption based on a waiting time of 80 minutes.


```{r}
predict(faithful_lm, newdata = data.frame(waiting=c(80)))
```
Q7. Use the fitted model to predict the duration of an eruption based on a waiting time of 120 minutes.

```{r}
predict(faithful_lm, newdata = data.frame(waiting=c(120)))

```


Q8. Of the predictions that you made for 80 and 120 minutes, which is more reliable?
```{r}
range(faithful$waiting)
```


Q9. Calculate the RSS for the fitted model.

```{r}
summary(lm(faithful))
sum(residuals(faithful_lm)^2)
```

Q10. What proportion of the variation in eruption duration is explained by the linear relationship with waiting time?

```{r}
summary(faithful_lm)$r.squared

```
Q11. Calculate the standard deviation of the residuals of the fitted model.

```{r}
summary(faithful_lm)$sigma

```
Q12. Suppose both least squares and maximum likelihood are used to fit a simple linear regression model to the same data. The estimates for the slope and the intercept will be:


* The same
* Different
* Possibly same or different depending on data
```{r}
# answer is A
```

Q13. Consider the fitted regression model:
hat(y) =−1.5+2.3x
Select all of the following that must be true.

* There are observations in the dataset used to fit this regression with negative yy values.
* The difference between the yy values of observations at x = 10x=10 and x = 9x=9 is 2.3.
* A good estimate for the mean of YY when x = 0x=0 is -1.5.

```{r}
#Answer is C
```

Q14. Select all of the following that are true:
* The SLR model assumes that the relationship between the response and the predictor is linear.
* The SLR model assumes that the response variable follows a normal distribution.
* The SLR model allows for larger variances for larger values of the predictor variable.
* The SLR model assumes that errors are independent.

```{r}
# Answer is A and D
```

Q15. Suppose you fit a simple linear regression model and obtain 
hat(Beta) = 0 

Does this mean that there is no relationship between the response and the predictor?
* Yes
* No
* Depends on the intercept
```{r}
# Answer is No
```

