---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. Consider testing for significance of regression in a multiple linear regression model with 9 predictors and 30 observations. If the value of the FF test statistic is 2.4, what is the p-value of this test?

```{r}
n=30
p=9
2*pf(2.4,p-1,n-p,lower.tail=FALSE)
```

Q2. What is the p-value for testing $H_0: \beta_1 = 0 \ \text{vs} \ H_1: \beta_1 \neq 0$ in a multiple linear regression model with 5 predictors and 20 observations if the value of the t test statistic is -1.3?

```{r}
n=20
p=5
2*pf(1.3^2, p-1,n-p,lower.tail=FALSE)
```

Q3. Consider the true model

$Y = 3 + 2 x_1 + 0.5 x_2 + 5 x_3 + \epsilon$
$ \epsilon \sim N(0, \sigma^2 = 9)$

What is $\text{SD}[\hat{\beta}_2]$ given the values of predictors above?

```{r}
set.seed(42)
x_values = data.frame(
  x1 = runif(15),
  x2 = runif(15),
  x3 = runif(15)
)
b0=3
b1=2
b2=.5
b3=5
sig=3
X = cbind(x0=rep(1, 15),x_values)

C <- solve(t(X) %*% as.matrix(X))

sd_b2 = 3 * sqrt(C[3, 3])
sd_b2
```


For Questions 4-11, use the swiss dataset, which is built into R.

Fit a multiple linear regression model with Fertility as the response and the remaining variables as predictors. You should use ?swiss to learn about the background of this dataset.

Q4. Use your fitted model to make a prediction for a Swiss province in 1888 with:

54% of males involved in agriculture as occupation
23% of draftees receiving highest mark on army examination
13% of draftees obtaining education beyond primary school
60% of the population identifying as Catholic
24% of live births that live less than a year

```{r}
fit = lm(Fertility~ ., data=swiss)
betas= coef(summary(fit))[,1]

X = data.frame(1, 54, 23, 13, 60, 24)
y=as.matrix(X) %*% as.matrix(betas)
y
```

Q5. Create a 99% confidence interval for the coefficient for Catholic. Report the upper bound of this interval.
```{r}
fit = lm(Fertility~ ., data=swiss)
confint(fit, level=.99)["Catholic",]
```


Q6. Calculate the p-value of the test $H_0: \beta_{\text{Examination}} = 0 \ \text{vs} \ H_1: \beta_{\text{Examination}} \neq 0$

```{r}
fit = lm(Fertility~ ., data=swiss)
coef(summary(fit))
```


Q7. Create a 95% confidence interval for the average Fertility for a Swiss province in 1888 with:

40% of males involved in agriculture as occupation
28% of draftees receiving highest mark on army examination
10% of draftees obtaining education beyond primary school
42% of the population identifying as Catholic
27% of live births that live less than a year
Report the lower bound of this interval.

```{r}
fit = lm(Fertility~ ., data=swiss)
newdata=data.frame("Agriculture"=40, "Examination" = 28, "Education" = 10, "Catholic" = 42, "Infant.Mortality" = 27)

predict(fit, newdata = newdata, interval="confidence", level = .95)

```

Q8. Create a 95% prediction interval for the Fertility of a Swiss province in 1888 with:

40% of males involved in agriculture as occupation
28% of draftees receiving highest mark on army examination
10% of draftees obtaining education beyond primary school
42% of the population identifying as Catholic
27% of live births that live less than a year
Report the lower bound of this interval.

```{r}
fit = lm(Fertility~ ., data=swiss)
newdata=data.frame("Agriculture"=40, "Examination" = 28, "Education" = 10, "Catholic" = 42, "Infant.Mortality" = 27)

predict(fit, newdata = newdata, interval="prediction", level = .95)
```

Q9. Report the value of the FF statistic for the significance of regression test.
```{r}
fit = lm(Fertility~ ., data=swiss)
summary(fit)$fstatistic
```

Q10. Carry out the significance of regression test using α=0.01. What decision do you make?


a) Fail to reject H_0
b) Reject H_0
c) Reject H_1
d) Not enough information

```{r}
fit = lm(Fertility~ ., data=swiss)
summary(fit)
```

Answer. Reject H0


Q11. Consider a model that only uses the predictors Education, Catholic, and Infant.Mortality. Use an FF test to compare this with the model that uses all predictors. Report the p-value of this test.
```{r}
fit = lm(Fertility~ ., data=swiss)
fit_null = lm(Fertility~Education+Catholic+Infant.Mortality, data=swiss)
anova(fit_null, fit)
```

Answer 0.05628 


Q12. Consider two nested multiple linear regression models fit to the same data. One has an R^2 of 0.9 while the other has an R^2 of 0.8. Which model uses fewer predictors?


a) The model with an R^2 of 0.9
b) The model with an R^2R of 0.8
c) Not enough informaiton



Answer. The model with R^2 of .8


Q13. The following multiple linear regression is fit to data

$Y = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \epsilon$

If $\hat{\beta}_1 = 5$ and $\hat{\beta}_2 = 0.25$ then

a) The p-value for testing $H_0: \beta_1 = 0 \ \text{vs} \ H_1: \beta_1 \neq 0$ will be larger than the p-value for testing $H_0: \beta_2 = 0 \ \text{vs} \ H_1: \beta_2 \neq 0$

b) The p-value for testing $H_0: \beta_1 = 0 \ \text{vs} \ H_1: \beta_1 \neq 0$ will be smaller than the p-value for testing $H_0: \beta_2 = 0 \ \text{vs} \ H_1: \beta_2 \neq 0$

c) Not enough information

Answer. Not enough informaiton


Q14. Suppose you have an SLR model for predicting IQ from height. The estimated coefficient for height is positive. Now, we add a predictor for age to create an MLR model. After fitting this new model, the estimated coefficient for height must be:

a) Exactly the same as the SLR model
b) Different, but still positive
c) Zero
d) Negative
e) None of the above

Answer. None of the above


Q15. The following multiple linear regression is fit to data

$Y = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \epsilon$

If the F test for the significance of regression has a p-value less than 0.01, then we know that:


a) The p-values for both $H_0: \beta_1 = 0 \ \text{vs} \ H_1: \beta_1 \neq 0$ and $H_0: \beta_2 = 0 \ \text{vs} \ H_1: \beta_2 \neq 0$ will be less than 0.01.


b) The p-values for both $H_0: \beta_1 = 0 \ \text{vs} \ H_1: \beta_1 \neq 0$ and $H_0: \beta_2 = 0 \ \text{vs} \ H_1: \beta_2 \neq 0$ could be greater than 0.01.


c) $H_0: \beta_1 = 0 \ \text{vs} \ H_1: \beta_1 \neq 0$ will have a p-value less than 0.01 if $H_0: \beta_2 = 0 \ \text{vs} \ H_1: \beta_2 \neq 0$ has a p value greater than .01

Answer B
wrong Answer. C











