---
title: "Project Proposal"
output:
  html_document: 
    theme: readable
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Names of the students

Sunil Nandamuri(sunilkn2@illinois.edu) and Praveen Purohit(purohit4@illinois.edu)

### Project title

House Price Prediction

### Description of the data file

The dataset is split into training data with 1460 observation and test data which is 1459 observations. These combined make 2919 observations which meet the minimum 2000 observations criteria.

```{r}

train_df <- read.csv("train.csv")
str(train_df)
```

###  Background on the dataset

The dataset is from Kaggle. Link is https://www.kaggle.com/c/house-prices-advanced-regression-techniques/data

### Statement of personal interest

Personal Interest -  We wish to start on Kaggle competitions and this is supposed to be a good kickstarter dataset. We intend to submit this on Kaggle post completion of the project


### Evidence that data can be loaded into R

```{r}
head(train_df)

```

