---
title: "Week3_Practice Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("statsr")
library("dplyr")
```

Q1.Consider a random variable X that has a t distribution with 7 degrees of freedom. Calculate P[X > 1.3]
```{r}
pt(1.3,df=7,lower.tail = FALSE)
```

Q2. Consider a random variable Y that has a t distribution with 9 degrees of freedom. Find c such that P[X > c] = 0.025
```{r}
qt(.025,df=9,lower.tail = FALSE)
```
#TODO - why Y and then find P(X)


Q3. For this exercise, use the built-in trees dataset in R. Fit a simple linear regression model with Girth as the response and Height as the predictor. What is the p-value for testing $H_0: \beta_1 = 0$ vs $H_1: \beta_1 \neq 0$?

```{r}
m1 <- lm(Girth~Height, data = trees)
coef(summary(m1))["Height", "Pr(>|t|)"]
```

Q4. Continue using the SLR model you fit in Question 3. What is the length of a 90% confidence interval for $\beta_1$?

```{r}
m1 <- lm(Girth~Height, data = trees)
diff(c(confint(m1, parm = "Height", level=.9)))


```

Q5. Continue using the SLR model you fit in Question 3. Calculate a 95% confidence interval for the mean tree girth of a tree that is 79 feet tall.

Report the upper bound of this interval.
```{r}
m1 <- lm(Girth~Height, data = trees)
predict(m1, newdata = data.frame("Height" = c(79)), interval = c("confidence"), level = .95)[1,"upr"]
```


