---
title: "Week3_Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Q1. Consider a random variable X that has a t distribution with 5 degrees of freedom. Calculate P[|X| > 2.1]


```{r}
pt(2.1, df = 5,lower.tail = FALSE)
# above is incorrect. 

# Correct answe r - The question asks for the probability that the absolute value of X is greater than 2.1, so it should be a two-tailed test.

2*pt(2.1, df = 5,lower.tail = FALSE)



```

Q2. Calculate the critical value used for a 90% confidence interval about the slope parameter of a simple linear regression model that is fit to 10 observations. (Your answer should be a positive value.)
```{r}
qt(.95,8)
```

Q3. Consider the true simple linear regression model  
$Y_i=5+4x_i+ϵ_i$    
$ϵ_i∼N(0, σ^2=4)$   
$i=1,2,…20$   

Given $S_{xx} = 1.5$, calculate the probability of observing data according to this model, fitting the SLR model, and obtaining an estimate of the slope parameter greater than 4.2.

In other words, calculate $P[\hat{\beta}_1 > 4.2]$.

```{r}
# The below answer is wrong
pnorm(4.2, mean=4, sd=sqrt(2), lower.tail = FALSE)

#Try this approach
#Please notice V(β^1)=σ2/Sxx′ 
pnorm(4.2, mean=4, sd=sqrt(4/1.5), lower.tail = FALSE)


```
```{r}

```

For Questions 4-11, use the faithful dataset, which is built into R.


Q4. Suppose we would like to predict the duration of an eruption of the Old Faithful geyser in Yellowstone National Park based on the waiting time before an eruption. Fit a simple linear model in R that accomplishes this task.

What is the value of $\text{SE}[\hat{\beta}_1]$?

```{r}
library(statsr)
library(dplyr)
m1 <- lm(eruptions~waiting, data=faithful)
coef(summary(m1))["waiting","Std. Error"]
```

Q5. What is the value of the test statistic for testing $H_0: \beta_0 = 0$  vs $H_1: \beta_0 \neq 0$ ?
```{r}
m1 <- lm(eruptions~waiting, data=faithful)
coef(summary(m1))["(Intercept)","t value"]
```

Q6. What is the value of the test statistic for testing $H_0: \beta_1 = 0$  vs $H_1: \beta_1 \neq 0$ ?
```{r}
m1 <- lm(eruptions~waiting, data=faithful)
coef(summary(m1))["waiting","t value"]
```

Q7. Test  $H_0: \beta_1 = 0$  vs $H_1: \beta_1 \neq 0$  with α=0.01. What decision do you make?
```{r}
m1 <- lm(eruptions~waiting, data=faithful)
beta_1_hat <- coef(summary(m1))["waiting", "Estimate"]
beta_1_hat_se <- coef(summary(m1))["waiting", "Std. Error"]
alpha=.01
n <- nrow(faithful)

pt(beta_1_hat, df=n-2)
confint(m1, parm = c("waiting"), level = .99)

#Todo dont know why this question is righ or wrong
```
Answer is Reject H0. WHY IS THAT THE ANSWER?


Q8. Calculate a 90% confidence interval for $\beta_0$
 . Report the upper bound of this interval.
```{r}
m1 <- lm(eruptions~waiting, data=faithful)

confint(m1, parm="(Intercept)", level = .9)[,2]
```
 
 Q9. Calculate a 95% confidence interval for $\beta_1$
 . Report the length of the margin of this interval
 
```{r}
m1 <- lm(eruptions~waiting, data=faithful)
diff(c(confint(m1, parm="waiting")))
# above answer is incorrect since the question is length of margin
# margin is same as margin of error
# CI = point estimate +- margin of error
# hence margin of error OR margin is half of confidence interval
# correct anser is below
diff(c(confint(m1, parm="waiting")))/2

```
 
 Q10. Create a 90% confidence interval for the mean eruption duration for a waiting time of 81 minutes. Report the lower bound of this interval.
```{r}
m1 <- lm(eruptions~waiting, data=faithful)
predict(m1, newdata = data.frame(waiting= 81), interval = c("confidence"), level = .9)[,"lwr"]
```

Q11. Create a 99% prediction interval for a new observation's eruption duration for a waiting time of 72 minutes. Report the upper bound of this interval

```{r}
m1 <- lm(eruptions~waiting, data=faithful)
predict(m1, newdata = data.frame(waiting= 72), interval = c("prediction"), level = .99)[,"upr"]
```
 
 Q12. Consider a 90% confidence interval for the mean response and a 90% prediction interval, both at the same xx value. Which interval is narrower?
 
 Ans. Confidence interval
  
  
Q13. Suppose you obtain a 99% confidence interval for β1 that is (-0.4, 5.2)(−0.4,5.2). Now test H_0: \beta_1 = 0 vs H_1: \beta_1 \neq 0 with α=0.01. What decision do you make?

Ans. Fail to reject H0


Q14. Suppose you test H_0: β1=0 vs H_1:β1 not=0 with α=0.01 and fail to reject H_0
 . Select all of the following that must always be true:
1) We would also fail to reject at α=0.05
2) There is no relationship between the response and the predictor.
3) The probability that β1=0 is very high.
4) The probability of observing the estimated value of β1 (or something more extreme) is greater than 0.01 if we assume that β1=0.
5) The value of β1 is very small. For example, it could not be 1.2.

Ans. 
Option 3 should not be selected since beta1 is not an estimate, it is universal model and hence probability concept is not applicable to is.

Option 4 is the definition of p value

Answer Only 4 is the correct option



Q15. Consider a 95% confidence interval for the mean response calculated at x = 6. If instead we calculate the interval at x = 7, select each value that would change:

1) Critical Value
2) Estimate
3) Standard Error

Answer: 
wrong ansers
1) Critical value and Estimate
2) crtical value and Standard error
3) All three





