---
title: "Week8 Quiz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
data_1 <- read.csv("data1.csv")
data_2 <- read.csv("data2.csv")
library(ggplot2)
```

1.Question 1

The above code block has access to two data frames named data_1 and data_2, both with variables y and x. Here, we use y as the response.

Fit a simple linear regression to both datasets. For both fitted regressions, create a Normal Q-Q plot.


```{r}
m1 <- lm(y~x, data = data_1)
m2 <- lm(y~x, data = data_2)

```
```{r}
ggplot(data = data_1, aes(sample=y)) + stat_qq() + stat_qq_line()
ggplot(data = m1, aes(sample=m1$model$y)) + stat_qq() + stat_qq_line()
```

```{r}
ggplot(data = data_2, aes(sample=y)) + stat_qq() + stat_qq_line()
```


Based on the plots which is true:

* The normality assumption is more suspect for the model fit to data_1.
* The normality assumption is more suspect for the model fit to data_2. - ANSWER


2.Question 2
The above code block has access to two data frames named data_1 and data_2, both with variables y and x. Here, we use y as the response.

Fit a simple linear regression to both datasets. For both fitted regressions, create a Fitted versus Residuals plot.

Based on the plots which is true:
```{r}
ggplot(data = m1, aes(x = fitted(m1), y = resid(m1))) +
  geom_point(size = 2) + geom_hline(yintercept=0)
```

```{r}
ggplot(data = m2, aes(x = fitted(m2), y = resid(m2))) +
  geom_point(size = 2) + geom_hline(yintercept=0)
```

* The equal variance assumption is more suspect for the model fit to data_1. - ANSWER
* The equal variance assumption is more suspect for the model fit to data_2.



3.Question 3
Consider the model $Y = 2 + 4 x + \epsilon$
where $\epsilon \sim N(0, \sigma^2 = x ^ 2)$

That is $\text{Var}[Y \mid X = x] = x ^ 2$

Calculate $P[Y < -12 \mid X = -3]$
```{r}
# fit x=-3 to calculate y
y=2+4*-3
sd=sqrt((-3)^2)
pnorm(-12, mean = y, sd=sd)

```


4.Question 4
For Questions 4-9, use the LifeCycleSavings dataset that is built into R.

Fit a multiple linear regression model with sr as the response and the remaining variables as predictors. What proportion of observations have a standardized residual less than 2 in magnitude?


```{r}
m <- lm(formula = sr ~ . , data=LifeCycleSavings)
mean(abs(rstandard(m))<2)
```



5.Question 5

Continue using the model fit in Question 4. Note that each observation is about a particular country. Which country (observation) has the standardized residual with the largest magnitude?

```{r}
which.max(rstandard(m))
```


6.Question 6

Continue using the model fit in Question 4. How many observations have “high” leverage? Use twice the average leverage as the cutoff for “high.”

```{r}
sum(hatvalues(m)>2*mean(hatvalues(m)))

```



7.Question 7

Continue using the model fit in Question 4. Which country (observation) has the largest leverage?
```{r}
which.max(hatvalues(m))
```



8.Question 8

Continue using the model fit in Question 4. Report the largest Cook’s distance for observations in this dataset.

```{r}
max(cooks.distance(m))
```


9.Question 9

Continue using the model fit in Question 4. Find the observations that are influential. Use $\frac{4}{n} $
  as the cutoff for labeling an observation influential.

Create a subset of the original data that excludes these influential observations and refit the same model to this new data. Report the sum of the estimated $\beta$ coefficients.

```{r}
influentials <- names(cooks.distance(m)[(cooks.distance(m)>4/nrow(m$model))])
LifeCycleSavings$country <- rownames(LifeCycleSavings)
LifeCycleSavings_wo_influentials <- LifeCycleSavings[!(LifeCycleSavings$country %in% influentials),]
LifeCycleSavings_wo_influentials <- subset(LifeCycleSavings_wo_influentials, select = -c(country) )

m_noinf <- lm(formula = sr ~ . , data = LifeCycleSavings_wo_influentials)
sum(coef(m_noinf))
```


10.Question 10
For Questions 10-15, use the airquality dataset that is built into R. For simplicity, we will remove any observations with missing data. We will use Ozone as the response and Temp as a single predictor.

```{r}
airquality <- na.omit(airquality)
```


$Y = \beta_0 + \beta_1 x + \beta_2 x^2 + \epsilon$
Test for the significance of the quadratic term. Report the p-value of this test.

```{r}
m <- lm(formula = Ozone~Temp + I(Temp^2), data = airquality)
coef(summary(m))["I(Temp^2)", "Pr(>|t|)"]
```


11.Question 11
Fit the model

$Y = \beta_0 + \beta_1 x + \beta_2 x^2 + \beta_3 x^3 + \beta_4 x^4 + \epsilon$

Test to compare this model to the model fit in Question 10. Report the p-value of this test.

```{r}
m2 <- lm(formula = Ozone~ Temp + I(Temp^2) + I(Temp^3) + I(Temp^4), data = airquality)
anova(m, m2)$"Pr(>F)"[2]
```



12.Question 12

Use the Shapiro-Wilk test to asses the normality assumption for the model in Question 11. Use $\alpha = 0.01$
Select the correct decision and interpretation:

```{r}
shapiro.test(resid(m2))
```


* Fail to reject H_0 - Normality assumption is suspect.
* Fail to reject H_0 - Normality assumption is not suspect.
* Reject H_0 - Normality assumption is suspect. - ANSWER
* Reject H_0 - Normality assumption is not suspect.


13.Question 13
Fit the model

$\log(y) = \beta_0 + \beta_1 x + \epsilon$

Use the Shapiro-Wilk test to asses the normality assumption for this model. Use $\alpha = 0.01$

```{r}
m3 <- lm(formula = log(Ozone)~Temp, data = airquality)
shapiro.test(resid(m3))
```

Select the correct decision and interpretation:

* Fail to reject H_0 - Normality assumption is suspect.
* Fail to reject H_0 - Normality assumption is not suspect.- ANSWER
* Reject H_0 - Normality assumption is suspect.
* Reject H_0 - Normality assumption is not suspect.


14.Question 14
Use the model from Question 13 to create a 90% prediction interval for Ozone when the temperate is 84 degrees Fahrenheit. Report the upper bound of this interval.

```{r}
# NOTE THAT YOU HAVE TO CONVERT THE PREDICT BACK INTO EXP
exp(predict(m3, interval = c("prediction"), newdata = data.frame(Temp=c(84)), level = .9))
```


15.Question 15
Using the model from Question 13, calculate the ratio of:

* The sample variance of residuals for observations with a fitted value less than 3.5
* The sample variance of residuals for observations with a fitted value greater than 3.5

(While not a formal test for the equal variance assumption, we would hope that this value is close to 1.)

```{r}
var(m3$residuals[m3$fitted.values<3.5])/var(m3$residuals[m3$fitted.values>3.5])


```

